\documentclass[../main.tex]{subfiles}
\begin{document}
\chapter*{Acknowledgements}

First and foremost, I would like to thank my family for their unwavering support and love. While I may
never be able to fully discuss my thesis with you, all that matters to me is the
closeness and love you never fail to share. Grazie.

I would like to thank my supervisor, Niklas, for his guidance and for devoting so much attention to
this thesis. I am quite sure that if it wasn't for Niklas, I would still be reading papers. Your
openness to a self-proposed topic, availability for weekly meetings, your contributions and feedback
on my ideas have all proven incredibly valuable. Thank you.

Similarly, I cannot continue without thanking my co-supervisor Juan. Thank you for agreeing to
supervise me as part of the SPAR programme, and for remaining available to the same extent well past
the end of the program. Our bi-weekly meetings were an excellent source of discussions and
idea-bouncing that proved to be very valuable. Thank you.

To Benita, thank you for your patience, your support and your affection. Most of all, thank you for
keeping me sane by reminding me to find a balance between work and life, staying healthy and
positive. Our calls, the times we spent cooking together, our travels, your letters and your company,
ever so fleeting, may not have seemed much, but proved to be essential. Gracias.

To my friends Victor, Karolina, Chase and Luuk: Thank you for keeping me company at the fifth floor
flexdesks, for sharing lunch by the third floor microwave or at Cafe Neo\footnote{this message was
	NOT sponsored by Cafe Neo.}, for the discussions on grounding and whatever goal misgeneralization is
supposed to be and for hyping me up when the results finally came. Thank you for being there. I love
you guys.

\thispagestyle{empty}% or plain etc.
\markboth{Acknowledgements}{Acknowledgements}
\end{document}
